Data Management for LSST Special Programs

### 2024-03-27 sec_intro.tex
add text for users

The three main takeaways for Rubin Data Management regarding Special Programs are:

@@

@@

Some science goals for Special Programs can be met with standard processing,
but some will require Special Processing by Rubin Data Management or user-generated processing.

@@

Guidelines for User-Generated Processing, and for user-generated data products
that can be federated with the Rubin-product data products (i.e., joinable tables),
is forthcoming.

>>>>

The three main takeaways for Rubin Data Management regarding Special Programs,
and a fourth takeaway that is a message mainly for Rubin users, are:

@@

\item There will be cases where User-Generated Processing is required to meet
science goals from Special Programs.
(Section~\ref{ssec:proc_user})

@@

Some science goals for Special Programs can be met with standard processing,
but some will require Special Processing by Rubin Data Management or User-Generated processing.

@@

Further details such as Rubin-provided support for User-Generated Processing is discussed
in Section~\ref{ssec:proc_user}.
